### 2015-04-17 draft.tex
..

\section*{Introduction}
% possibly in introduction instead?
Maple \cite{Maple} proposes a SDN controller model where the behavior of the controller is defined by a function from packets to forwarding path, the algorithmic policy. The authors then show how to optimize the controller so that packets are handled without having to run the function on them. Maple does so by providing a packet API capturing each access to packet fields, and memoizing the results of the function for subsequent packets sharing the accessed fields' values. We identify a number of shortcoming to this model:
\begin{enumerate}
\item % packet value granularity too fine
  \item % environmentgranularity too fine, no built-in support for dynamic controllers
  \item % not proactive
\end{enumerate}

@@

@@

\begin{figure}
\begin{lstlisting}
f(pkt):
  if RO.InRange(pkt, src, 0, 10) then
     if RO.InRange(pkt, dst, 0, 10) then
        RO.deliver()
     else 
        RO.add(pkt, (dst, src), trusted);
        RO.deliver()
  else if (RO.InSet(pkt, (src,dst), trusted) then
         RO.deliver()
       else
         RO.drop
       end
  end                
  \end{lstlisting}

@@

\section*{Algorithic Policies Revisited}
% Explains what algorithmic policies are, how maple was handling them and the difference with our model

>>>>

\section*{Introduction}

Maple \cite{Maple} proposes a SDN controller model where the behavior of the controller is defined by a function from packets to forwarding path, the algorithmic policy. The authors then show how to optimize the controller so that packets are handled without having to run the function on them. Maple does so by providing a packet API capturing each access to packet fields, and memoizing the results of the function for subsequent packets sharing the accessed fields' values. We identify a number of shortcoming to this model:
\begin{enumerate}
\item When a field value is observe, the forwarding decision only works on packets with this exact value, even if the forwarding decision is made on a much coarser range of value.Similarly, after observing some value in the environment, the forwarding decision is specialize for that particular value

\item It no built-in environment datastructure with automatic invalidation of decision trace when the environment is modified, which is needed to implement dynamic controllers.

  \item Populating the decision tree requires seeing a high number of packets, potentially slowing down the network at start-up. 
\end{enumerate}

@@

\section*{Algorithic Policies Revisited}
% Explains what algorithmic policies are, how maple was handling them and the difference with our model 
Algorithmic policies were introduced by Maple as a model for SDN controllers. An algorithmic policy consist of a function from packet to forwarding decision. Under this model, the network forwards packets as if this function was executed on each packet when entering the network.

@@

\begin{figure}
\begin{lstlisting}
f(pkt):
  if RO.in_range(pkt, src, 0, 10) then
     if RO.in_range(pkt, dst, 0, 10) then
        RO.deliver()
     else 
        RO.add(pkt, (dst, src), trusted);
        RO.deliver()
  else if (RO.in_set(pkt, (src,dst), trusted) then
         RO.deliver()
       else
         RO.drop
       end
  end                
  \end{lstlisting}

@@
